---
title: "Suppl. 2"
author: "Michael Soutschek"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  pdf_document: default
  html_document: default
---


```{r, include=FALSE}
if(!exists('FIG_NB')){
  FIG_NB <- 0
  getFigNb <- function(increment=FALSE){
    if(increment) FIG_NB <<- FIG_NB + 1
    FIG_NB
  }
}
knitr::opts_chunk$set(fig.width=8)
```

# `r getFigNb(TRUE)`



```{r, include=FALSE}
suppressPackageStartupMessages({
  library(ggplot2)
  library(cowplot)
  library(gridExtra)
  library(scales)
  library(GenomicRanges)
  library(S4Vectors)
  library(patchwork)
})
source("../../misc.R")
```


```{r, warning=FALSE}
df <- rbind(
  readRDS("cut_off_corr/allCors.HEK.new.rds"),
  readRDS("cut_off_corr/allCors.HeLa.new.rds") )
df0 <- df[df$cut_off==0,]
r20 <- setNames(df0$r2,df0$miRNA)
r20 <- r20[r20>0.1]
df <- df[df$miRNA %in% names(r20),]
df$prop.r <- sqrt(df$r2)/sqrt(r20)[df$miRNA]
df$prop.r2 <- df$r2/r20[df$miRNA]

m1 <- readRDS(file = "../../../Parameter_Optimization/data/hsa.12mirs.HEK.fullScan.GR.rds")
m2 <- readRDS(file = "../../../Parameter_Optimization/data/hsa.12mirs.HELA.fullScan.GR.rds")
m <- c(m1,m2)
names(cutoffs) <- cutoffs <- unique(df$cut_off)
propAbove <- sapply(cutoffs, FUN=function(x) sum(m$log_kd> (1000*x)))/length(m)

p1 <- ggplot(df, aes(cut_off, prop.r2)) + geom_line(aes(colour=miRNA)) + 
  geom_smooth(colour="black") + geom_vline(xintercept=-0.3, linetype="dashed") +
  labs(x=bquote(~log(K[D])~"cut-off"), y=bquote("Proportion of full"~r^2)) + theme_minimal()
p2 <- ggplot(data.frame(logkd=cutoffs, propAbove=propAbove), aes(logkd, propAbove)) + 
  geom_line() + ylab(bquote("Proportion of sites\nabove threshold")) + ylim(0,1) +
  xlab(bquote(~log(K[D])~"cut-off")) +
  annotate("point", x=-0.3, y=propAbove["-0.3"]) + 
  annotate("text", x=-0.35, y=propAbove["-0.3"]+0.15, label=paste0(round(100*propAbove["-0.3"]),"% reduction"), hjust=0) +
  theme(axis.title.x=element_blank(), axis.text.x=element_blank(), axis.ticks.x=element_blank()) + theme_minimal()
pp1 <- p2/p1 + plot_layout(heights=c(1,2))
```

```{r, include=FALSE}
# mods <- scanMiRData::getKdModels()
# topkd <- sapply(mods[names(r20)], FUN=function(x) mean(head(sort(x$mer8),20)/1000))
# df15 <- df[df$cut_off== -1.5,]
# df15$topKd <- topkd[as.character(df15$miRNA)]
# with(df15, cor.test(topKd, prop.r2))
```













```{r, include=FALSE}
# Cut off Corr

df1 <- readRDS("./cut_off_corr/PlotDF.rds")

p1 <- ggplot(df1, aes(x = cut_off, y = r2)) + 
  geom_line(size = 1) +
  theme_minimal() +
  ylab(expression(~r^2)) +
  xlab(bquote(~log(K[D])~"cut-off")) +
  facet_grid(~mir) +
  theme(
                panel.border =element_rect(color="black", fill=NA),
                text = element_text(size=12),
                legend.title = element_text(size = rel(0.9)),
                legend.text = element_text(size = rel(0.8))
  )


# Pie Chart

e <- as.data.frame(mcols(m))
e$transcript <- as.factor(seqnames(m))

cut_off <- nrow(e[e$log_kd > -300,])/nrow(e)
rest <- 1 - nrow(e[e$log_kd > -300,])/nrow(e)

df <- data.frame("cut" = cut_off , "rest" = rest)
df <- data.frame(t(df))
df$group <- c("Cut-off at -0.3","All other sites")


blank_theme <- theme_minimal()+
  theme(
  axis.title.x = element_blank(),
  axis.title.y = element_blank(),
  panel.border = element_blank(),
  panel.grid=element_blank(),
  axis.ticks = element_blank(),
  plot.title=element_text(size=14, face="bold"),
  legend.title = element_blank(),
  plot.margin = unit(c(0,2,0,1), "lines")
  )

pie <- ggplot(df, aes(x="", y=t.df., fill=group))+
  geom_bar(width = 1, stat = "identity") + 
  coord_polar("y", start=0) + 
  scale_fill_manual(values = c("#4477AA","#CC6677")) +
  blank_theme 

pie <- pie + theme(axis.text.x=element_blank(), legend.position = "bottom") + 
  geom_text(aes(y = t.df./2 + c(0, cumsum(t.df.)[-length(t.df.)]), 
                label = percent(t.df./100)), size=5)
```


```{r}
# Table

df2 <- readRDS("./cut_off_corr/Plot_Table_cut_df.rds")
p2 <- tableGrob(df2, rows = NULL, theme=ttheme_default(base_size=10))
```



```{r}
#Speed Figure

df4 <- readRDS("../../../Speed_Comparison/Speed_DF2.rds")

p4 <- ggplot(df4,aes(x = Sequences, y = time, color = Algorithm)) + 
  geom_line(aes(linetype = Condition)) + scale_x_log10() + 
  ylab("Time (s)") + theme_classic() + scale_color_manual(values = meth_cols2, guide="none") + 
  theme(plot.margin = unit(c(2,0.5,0,0), "lines"), legend.position = "bottom", legend.direction = "vertical")
```




```{r, fig.width=10, fig.height=8, message=FALSE}

pp2 <- plot_grid(p2,p4,ncol = 2, labels = c("B","C"))
plot_grid(pp1,pp2,labels = c("A",""), ncol = 1, rel_heights = c(1,0.85), scale = 0.95)
ggsave("Suppl_5.png",bg = "white",width = 10, height = 8)
```



### `r getFigNb()`

**Computational optimizations in scanMiR - Preliminary. A:** Proportion of maximal Pearson correlation values of predicted and measured miRNA repression depending on different maximal $K_D$-values (“cutoff”) for all miRNAs transfected in HEK & HeLa with an $r^2$-value of at least 10% from the study of McGeary and colleagues (2019). MiR-216b-5p is the only miRNA displayed with a reduction of more than 2.5% of its maximal $r^2$-value with a cutoff of -0.3. The black line indicates the smoothed mean. Potential reductions in site numbers across the spectrum of indicated cutoffs are shown in the upper panel. **B:** The maximum $log(K_D)$ cutoff-values for the 12 miRNAs used in HEK-transfection experiments (McGeary et al., 2019) which cause a diminution of the correlation by only 2.5% (= Cut-off 97.5%) or 1% (= Cut-off 99%), respectively. For individual miRNAs, there were pronounced variations in the cutoff beyond which the addition of binding sites with a lower affinity did not substantially improve the correlation between predicted and observed repression. **C:** Run times of the scanning algorithm of McGeary et al. (2019) with and without folding of the transcripts.
