---
title: "Suppl_4"
author: "Michael Soutschek"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---



```{r, include=FALSE}
if(!exists('FIG_NB')){
  FIG_NB <- 0; FIG_STRING <- "Supplementary Figure S"
  getFigNb <- function(increment=FALSE){
    if(increment) FIG_NB <<- FIG_NB + 1
    paste0(FIG_STRING,FIG_NB)
  }
}
knitr::opts_chunk$set(fig.width=8)
```

# `r getFigNb(TRUE)`


```{r, include=FALSE}
suppressPackageStartupMessages({
  library(ggplot2)
  library(cowplot)
})
source("../../misc.R")
```

```{r, include=FALSE}
Rims3 <- readRDS("Rims3_dist.rds")
Rims3$logKd <- Rims3$log_kd / 1000
Rims3$type <- ifelse(Rims3$type == "non-canonical","",as.character(Rims3$type))
Rims3$type <- ifelse(grepl("6mer",Rims3$type),"",as.character(Rims3$type))
Rims3 <- Rims3[Rims3$logKd < -1,]

p1 <- ggplot(Rims3, aes(x = start, y = -`logKd`)) + 
        geom_hline(yintercept=1, linetype="dashed", color = "red", size=1) + 
        geom_point(size=2) + geom_text(label = Rims3$type,nudge_y = 0.1) + 
        geom_point(data = Rims3[Rims3$start == 1061,],size = 4, shape = 1) +
        facet_wrap("dist",nrow = 2) + 
        xlab("UTR length")+ ylab("-log(Kd)") + theme_light() + theme(
          strip.text.x = element_text(size = 12,color = "black"),
          plot.margin = unit(c(2,2,2,2), "lines")
        ) + ggtitle("Rat NM_022931 - miR-138-5p")

```

```{r, fig.width=8, fig.height=6}
p1
```




### `r getFigNb()`

**Removal of overlapping sites in scanMiR.** Users can specify a minimum allowed distance between binding sites of the same miRNA. Within that distance, scanMiR automatically keeps only the site with the highest affinity, as shown here for miR-138-5p binding sites on a rat Rims3 transcript. An example site removed due to a nearby higher-affinity site is highlighted.
