---
title: "Suppl1"
author: "Michael Soutschek"
date: "3/29/2021"
output: html_document
---


```{r, include=FALSE}
if(!exists('FIG_NB')){
  FIG_NB <- 0; FIG_STRING <- "Supplementary Figure S"
  getFigNb <- function(increment=FALSE){
    if(increment) FIG_NB <<- FIG_NB + 1
    paste0(FIG_STRING,FIG_NB)
  }
}
knitr::opts_chunk$set(fig.width=8)
```

# `r getFigNb(TRUE)`



```{r, include=FALSE}
suppressPackageStartupMessages({
  library(ggplot2)
  library(cowplot)
  library(viridis)
  library(grid)
  library(gridExtra)
})
source("../../misc.R")
```


```{r, include=FALSE}

df <- readRDS("../../../Revision/Targetscan8_correlation/BarGraph_DF_HEK_revision.rds")
df <- df[df$type != "scanMiR hg38 utr", ]
df <- df[df$type != "scanMiR hg38 utr can.", ]
df <- df[df$type != "scanMiR hg38 can.", ]


mirs <- levels(as.factor(as.character((df$miRNA))))

col1 <- rev(RColorBrewer::brewer.pal(11, "Blues")[c(3,5,7,9)])
col2 <- rev(RColorBrewer::brewer.pal(11, "Greens")[c(3,5,7,9)])
col3 <- rev(RColorBrewer::brewer.pal(8, "Greys")[c(3,5,7)])
cols <- c(col1,col2,col3)

plot_list <- list()
for(i in mirs){
  dfi <- df[df$miRNA == i,]
  p <- ggplot(dfi, aes(miRNA, r2, fill = type)) + 
          geom_col(position="dodge", show.legend = FALSE) +
          theme_classic() +
          ggtitle(i) +
          theme(axis.text.x=element_blank(),
                axis.ticks.x=element_blank(),
                axis.title = element_blank(),
                plot.title = element_text(hjust = 0.5)) +
          #scale_fill_viridis_d(alpha = 0.8) +
          scale_fill_manual(values = cols) +
          scale_y_continuous(expand = c(0, 0), limits = c(0,0.325), breaks = c(0,0.05,0.1,0.15,0.2,0.25,0.3) ) 
  plot_list[[i]] <- p
}

p1 <- ggplot(df, aes(miRNA, r2, fill = type)) + 
          geom_col(position="dodge", show.legend = TRUE) +
          theme_classic() +
          ggtitle(i) +
          theme(axis.text.x=element_blank(),
                axis.ticks.x=element_blank(),
                axis.title = element_blank(),
                plot.title = element_text(hjust = 0.5),
                legend.position = "bottom",
                legend.title = element_blank(),
                legend.spacing.x = unit(0.5, 'cm')) +
          guides(fill=guide_legend(nrow=3,byrow=TRUE)) +
           #scale_fill_viridis_d(alpha = 0.8) +
          scale_fill_manual(values = cols) +
          scale_y_continuous(expand = c(0, 0), limits = c(0,0.325), breaks = c(0,0.05,0.1,0.15,0.2,0.25,0.3) ) 

legend <- get_legend(
  # create some space to the left of the legend
  p1
)
```


```{r, include=FALSE}
pp1 <- plot_grid(plotlist =  plot_list, ncol = 4) 
y.grob <- textGrob(bquote("Correlation with observed repression"~(r^2)),gp=gpar(fontsize=15),rot=90)
pp1 <- grid.arrange(arrangeGrob(pp1, left = y.grob))
pp2 <- plot_grid(pp1,legend,ncol = 1, rel_heights = c(4,1))
ggsave("Suppl_2.png",height = 10, width = 11, bg = "white")
```

```{r,fig.width=11, fig.height=10}
pp2
```


### `r getFigNb()`

**Comparison of scanMiR repression predictions versus TargetScan8 occupancy scores.** Pearson correlations of scanMiR repression predictions and TargetScan8 (TS8) occupancy scores with measured mRNA changes following miRNA mimic transfections in HEK cells (McGeary et al., 2019). The first four bars for each miRNA indicate the correlations of default scanMiR repression predictions obtained with different genome annotations (hek = Custom HEK cell annotation from McGeary et al. (2019), hg19 = GRCh37, hg38 = GRCh38 & TS ann. = Custom human 3'UTR annotation obtained from TargetScan8). To comprehensively compare scanMiR repression scores to TargetScan8 occupancy scores, we further included analyses considering either exclusively canonical sites ("can."), only sites in the 3'UTR ("utr") or a combination of both. The last three bars show the Pearson correlations of occupancy scores (for low and high abundant miRNAs as well as transfected miRNAs) provided in the latest TargetScan update (version 8) with the same measured mRNA logFC. All scanMiR repression predictions are calculated with the globally optimized a-value (see Fig. 3C).
