---
title: "Suppl. Affinity"
author: "Michael Soutschek"
date: "16 5 2021"
output:
  pdf_document: default
  html_document: default
---

```{r, include=FALSE}
if(!exists('FIG_NB')){
  FIG_NB <- 0; FIG_STRING <- "Supplementary Figure S"
  getFigNb <- function(increment=FALSE){
    if(increment) FIG_NB <<- FIG_NB + 1
    paste0(FIG_STRING,FIG_NB)
  }
}
knitr::opts_chunk$set(fig.width=8)
```

```{r, include=FALSE}
suppressPackageStartupMessages({
  library(scanMiR)
  library(scanMiRData)
  library(ggplot2)
  library(cowplot)
  library(grid)
})
source("../../misc.R")
```

# `r getFigNb(TRUE)`

```{r, include=FALSE}
hsa <- getKdModels(species = "hsa")
hsa_499 <- hsa[["hsa-miR-499a-5p"]]
hsa_129 <- hsa[["hsa-miR-129-5p"]]
hsa_155 <- hsa[["hsa-miR-155-5p"]]
op <- par()
par(mar=c(0,0,0,0))
p1 <- plotKdModel(hsa_499,"logo")
p2 <- plotKdModel(hsa_129,"logo")
p3 <- plotKdModel(hsa_155, what = "seeds") + 
  guides(fill=guide_legend(nrow=2,byrow=TRUE,title.position = "top")) +
  theme_minimal() + theme(
    axis.text.y = element_text(family="mono", size = 10),
    plot.subtitle=element_text(family="mono"),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.x = element_blank(),
    legend.position = "bottom") 
p3 <- p3 + scale_fill_manual(values = type_cols[p3$data$type])
```


```{r, include=FALSE}
#mods
mods <- scanMiRData::getKdModels("hsa",NULL)
mods_124 <- mods[["hsa-miR-124-3p"]]

#Mink1
Mink1 <- readRDS("BindingExamples/Mink1_124.rds")
Mink1_df <- as.data.frame(Mink1)

p5 <- as_grob(~viewTargetAlignment(Mink1[2],mods_124,flagBulgeMatches=TRUE, outputType = "plot",cex=1.05))

# Mink1 table

# Mink1_table <- Mink1_df[order(Mink1_df$start),c("seqnames","start","end","type")]
# tt2 <- ttheme_default(core=list(fg_params=list(hjust=1, x=0.9)),
#                       rowhead=list(fg_params=list(hjust=1, x=0.95)),
#                       base_size = 11)
# g2 <- tableGrob(Mink1_table,rows = NULL,theme = tt2)
# g2 <- gtable_add_padding(g2, unit(c(0,15,5,0), "mm"))
```





```{r, include=FALSE}
bl <- ggplot() + theme_void()
pp1 <- plot_grid(p1,p2,nrow = 2,labels = c("miR-499a-5p","miR-129-5p"), scale=0.95,
                 label_fontface = 0, hjust = 0, label_x = 0.5)
pp1 <- plot_grid(pp1,p3,ncol = 2,labels = c("A","B"))

pp2 <- plot_grid(bl,p5,bl,ncol = 3,labels = c("","C",""), rel_widths = c(1,5,1))
pp2 <- pp2 + draw_text("miR-124-3p g-bulged 7mer site at nt 723 of Mink1", x = 0.25, y = 0.8, hjust = 0, fontface = "italic", size = 11) 

pp <- plot_grid(pp1,pp2,ncol = 1,labels = "",rel_heights = c(1.5,0.7))
#ggsave("Suppl_1.png",height = 9, width = 10, bg = "white")
```

```{r, fig.height=9, fig.width=10}
pp
```



### `r getFigNb()`

**ScanMiR plotting functions provide insights into miRNA biology. A:** Nucleotide information content plots of miR-499a-5p and miR-129-5p. The information content of each nucleotide is calculated by its occurrence in the top ten seed complements with the lowest dissociation constants. **B:** Affinity plot of miR-155-5p showing a 'wobbled 7mer' as highest ranking non-canonical seed complement. **C:** scanMiR flags g-bulged miRNA binding sites in scan results and correctly represents target alignments of those sites (here shown for the experimentally validated miR-124-3p binding site on Mink1).
