---
title: "Suppl. Affinity"
author: "Michael Soutschek"
date: "16 5 2021"
output: html_document
---

```{r, include=FALSE}
if(!exists('FIG_NB')){
  FIG_NB <- 0; FIG_STRING <- "Supplementary Figure S"
  getFigNb <- function(increment=FALSE){
    if(increment) FIG_NB <<- FIG_NB + 1
    paste0(FIG_STRING,FIG_NB)
  }
}
knitr::opts_chunk$set(fig.width=8)
```

```{r, include=FALSE}
suppressPackageStartupMessages({
  library(scanMiR)
  library(scanMiRData)
  library(ggplot2)
  library(cowplot)
  library(grid)
})
source("../../misc.R")
```

# `r getFigNb(TRUE)`

```{r, include=FALSE}
hsa <- getKdModels(species = "hsa")
hsa_499 <- hsa[["hsa-miR-499a-5p"]]
hsa_129 <- hsa[["hsa-miR-129-5p"]]
hsa_155 <- hsa[["hsa-miR-155-5p"]]
op <- par()
par(mar=c(0,0,0,0))
p1 <- grid::grid.grabExpr(plotKdModel(hsa_499,"logo"))
p2 <- grid::grid.grabExpr(plotKdModel(hsa_129,"logo"))
p3 <- plotKdModel(hsa_155, what = "seeds") + 
  guides(fill=guide_legend(nrow=2,byrow=TRUE,title.position = "top")) +
  theme_minimal() + theme(
    axis.text.y = element_text(family="mono", size = 10),
    plot.subtitle=element_text(family="mono"),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.x = element_blank(),
    legend.position = "bottom") +
      scale_fill_manual(values = type_cols)
```


```{r, fig.height=3.8, fig.width=8}
pp1 <- plot_grid(p1,p2,nrow = 2,labels = c("miR-499a-5p","miR-129-5p"), scale=0.95,
                 label_fontface = 0, hjust = 0, label_x = 0.5)
plot_grid(pp1,p3,ncol = 2,labels = c("A","B"))
```

### `r getFigNb()`

**ScanMiR plotting functions provide insights into miRNA biology. A:** Nucleotide information content plots of miR-499a-5p and miR-129-5p. The information content of each nucleotide is calculated by its occurrence in the top ten seeds with the lowest dissociation constants. **B:** Affinity plot of miR-155-5p showing a 'wobbled 7mer' as highest ranking non-canonical seed.
