---
title: "Suppl_5"
author: "Michael Soutschek"
date: "16 4 2021"
output: html_document
---


```{r, include=FALSE}
if(!exists('FIG_NB')){
  FIG_NB <- 0; FIG_STRING <- "Supplementary Figure S"
  getFigNb <- function(increment=FALSE){
    if(increment) FIG_NB <<- FIG_NB + 1
    paste0(FIG_STRING,FIG_NB)
  }
}
knitr::opts_chunk$set(fig.width=8)
```

# `r getFigNb(TRUE)`


```{r, include=FALSE}
suppressPackageStartupMessages({
  library(ggplot2)
  library(cowplot)
  library(scanMiR)
  library(scanMiRData)
  library(scanMiRApp)
})
source("../../misc.R")
```


```{r, include=FALSE}
# Limk1

mods_rno <- scanMiRData::getKdModels("rno",NULL)
rno <- ScanMiRAnno(species = "Rnor_6")

#Scan and Prepare
mods_rno_134 <- mods_rno[["rno-miR-134-5p"]]
Limk1 <- getTranscriptSequence("ENSRNOT00000084427",annotation = rno, extract = "UTRonly")
Limk1_134_Gr <- findSeedMatches(Limk1,mods_rno_134,shadow = 15L,keepMatchSeq = TRUE,
                      p3.extra = TRUE,)

Limk1_134 <- as.data.frame(Limk1_134_Gr)

Limk1_134$logKd <- Limk1_134$log_kd / 1000
Limk1_134$type <- ifelse(Limk1_134$type == "non-canonical","",as.character(Limk1_134$type))
Limk1_134 <- Limk1_134[Limk1_134$logKd < -1,]
  
# get 8mer info
mer8 <- getSeed8mers(mods_rno_134$canonical.seed)
wA <- which(substr(mer8,8,8)=="A")
mer7 <- substr(mer8,1,7)
As <- mods_rno_134$mer8[wA]
names(As) <- mer7[wA]
mer.mean <- rowsum(mods_rno_134$mer8[-wA],mer7[-wA])[,1]/3
As <- As-mer.mean[names(As)]
d <- data.frame(seed=names(mer.mean), base=mer.mean/-1000, "A"=As[names(mer.mean)]/-1000,
          type=getMatchTypes(names(mer.mean),mods_rno_134$canonical.seed), row.names=NULL)
d <- d[head(order(d$base+d$A, decreasing=TRUE),n=1),]
mer8 <- d$base + d$A


p1 <- ggplot(Limk1_134, aes(x = start, y = -`logKd`)) + 
    geom_hline(yintercept=1, linetype="dashed", color = "red", size=1) + 
    geom_hline(yintercept=mer8, linetype="dashed", color = "gray64", size=1) + 
    geom_point(size=2) + geom_text(label = Limk1_134$type,nudge_y = -0.2) +
    geom_point(data = Limk1_134[Limk1_134$p3.score >5,], size = 4, shape = 1L) +
    xlab("UTR Sequence") + ylab(bquote("-"*log(K[D]))) +  xlim(0,width(Limk1)) +
    theme_light() + ggtitle("ENSRNOT00000084427 - miR-134-5p")

p2 <- as_grob(~viewTargetAlignment(Limk1_134_Gr[1],mods_rno_134,outputType = "plot",cex = 0.85))



#RBNS

acols <- c("#4477AA", "#117733", "#DDCC77", "#CC6677")
df2 <- readRDS("BarGraph_p3_DF_RBNS.rds")
df2$type <- gsub("ags","a",df2$type)

p3 <- ggplot(df2, aes(miRNA, r2, fill = type)) + 
  geom_col(position="dodge") +
  scale_fill_manual(values=acols) +
  theme_classic() + 
  theme(
                #panel.border =element_rect(color="black", fill=NA),
                text = element_text(size=12),
                legend.position = "none",
                # legend.title = element_text(size = rel(0.9)),
                # legend.text = element_text(size = rel(0.8)),
                axis.title.x=element_blank()
  ) +
  labs(fill = "Method") +
  ylab(bquote("Correlation with observed repression"~(r^2)))


# HEK


df3 <- readRDS("BarGraph_p3_DF_HEK.rds")
df3$type <- gsub("ags","a",df3$type)

p4 <- ggplot(df3, aes(miRNA, r2, fill = type)) + 
  geom_col(position="dodge") +
  scale_fill_manual(values=acols) +
  theme_classic() + 
  theme(
                #panel.border =element_rect(color="black", fill=NA),
                text = element_text(size=12),
                legend.title = element_text(size = rel(0.9)),
                legend.text = element_text(size = rel(0.8)),
                axis.title.x=element_blank(),
                axis.text.x = element_text(angle=45, hjust=1)
  ) +
  labs(fill = "Method") +
  ylab(bquote("Correlation with observed repression"~(r^2)))
```


```{r, fig.width=9, fig.height=8}
pp1 <- plot_grid(p1,p2,nrow=2, rel_heights = c(3,1))

pp2 <- plot_grid(pp1,p3,labels = "AUTO",ncol = 2, rel_widths = c(1.4,1))

plot_grid(pp2,p4,ncol = 1,labels = c("","C"),rel_heights = c(1,1.3))

ggsave("Suppl_7.png",height = 9,width = 8,bg = "white")
```



### `r getFigNb()`

**The 3’-supplementary score as well as length coefficients implemented in scanMiR slightly improve repression prediction. A:** Example miRNA binding site including extensive 3’-supplementary pairing. **B-C:** Pearson correlation values of observed and predicted repression in HeLA- (**B**) and HEK- (**C**) cells, including 3’-supplementary score as well as coefficients taking into account the open reading frame (ORF) and 3’UTR lengths of transcripts.