---
title: "Opt_log_kd_cutoff"
author: "Michael Soutschek"
date: "20 11 2020"
output: html_document
---


# Get the Load the Aggregate_Biochem Function directly here
```{r}
aggregateMatches_Biochem <- function(e , kd_cut_off = -0.3, ORF = TRUE, coef_back = 0, keepSiteInfo = FALSE){
  
  ag <- -5.013868
  b <- 0.8655766248703003
  c <- -1.848806619644165
  m <- as.data.frame(mcols(e))
  m$transcript <- as.factor(seqnames(e))
  m <- as.data.table(m)
  
  m$log_kd <- m$log_kd / 1000
  
  if(ORF) {
    m$c <- ifelse(m$ORF=="TRUE", c, 0)
    m$cut <- ifelse(m$ORF=="TRUE", (kd_cut_off  + c/2), kd_cut_off)
    m <- m[m$log_kd < m$cut,]
  }else{
    m$c <- 0
    m <- m[m$log_kd < kd_cut_off,]
  }
  
  #m <- m[m$log_kd < kd_cut_off,]
  m$ag <- ag
  m$log_ka <- -m$log_kd
  m$N <- 1 / (1 + exp(-1 * (m$ag + m$log_ka + m$c)))
  m$N_bg <- 1 / (1 + exp(-1 * (m$ag  + m$c + coef_back)))
  m_agg <- m[,.(N = sum(N),N_bg = sum(N_bg)),by = c("transcript","miRNA")]
  
  if(keepSiteInfo){
    m_agg2 <- dcast( m[,.(N=.N), by=c("transcript","miRNA","type")],
                     formula=transcript+miRNA~type, value.var="N", fill=0)
    m_agg <- merge(m_agg, m_agg2, by=c("transcript","miRNA"), all=TRUE)
  }
  
  m_agg$repression <- log(1 + exp(b)*m_agg$N_bg) - log(1 + exp(b)*m_agg$N)
  return(m_agg)
} 
```





# Correlation function
```{r}
get_cor_us <- function(cut_off, mir, return.raw = FALSE){
  
  # Get all files and connections
  m <- readRDS(file = "../../../../Parameter_Optimization/data/hsa.12mirs.HEK.fullScan.GR.rds")
  hek_tpm <- read.csv("../../../../Parameter_Optimization/data/McGeary_2019_raw/GSE140218_HEK293FT_transfection_logtpm_batchnormalized.txt", sep="\t", stringsAsFactors = F, row.names = 1)
  seeds <- gsub("\\.txt", "", list.files("/mnt/schratt/miRNA_KD/EnrichMir_Work/Aggregate_fg/predictions_anB/", full.names = F))
  
  # relate different miRNA IDs
  mirs_alt <- gsub("hsa-", "", seeds)
  mirs_alt <- gsub("-[35]p.*", "", mirs_alt)
  mirs_alt <- gsub("R-", "r", mirs_alt)
  
  seeds[seeds == "hsa-miR-184-3p"] <- "hsa-miR-184"
  names(mirs_alt) <- seeds
    
  
  # Get mean-centered hek-values and the aggregation
  # 1) get the seed info
  mir_seeds <- names(mirs_alt)[mirs_alt==mir]
  # 2) get the tpm values per mir
  subs_mir <- names(hek_tpm)[names(hek_tpm) != mir]
  hek_mir <- data.frame(
    logTPM = hek_tpm[[mir]]-rowMeans(hek_tpm[subs_mir]),
    transcript_id = row.names(hek_tpm),
    stringsAsFactors = F,
    row.names = rownames(hek_tpm)
    ) 
  
  # 3) aggregate
  m_agg <- aggregateMatches_Biochem(e = m, kd_cut_off = cut_off)
  m_agg_slim <- m_agg[,c(1,2,5)]
  m_repr <- pivot_wider(m_agg,id_cols = transcript, names_from = miRNA, values_from = repression, values_fill = list(repression = 0))
  m_repr <- column_to_rownames(m_repr, var = "transcript")

  # 4) get the correlation
  subs_mir2 <- names(mirs_alt)[mirs_alt!=mir]
  m_repr_mir <- m_repr[mir_seeds] - rowMeans(m_repr[subs_mir2], na.rm = TRUE)
  repr_mir <- merge(hek_mir,m_repr_mir,by = 0, all.x = TRUE )
  repr_mir[[mir_seeds]][is.na(repr_mir[[mir_seeds]])] <- 0
  if(return.raw) {
    return(repr_mir)
  }else{
    cor = cor.test(repr_mir[[mir_seeds]], repr_mir$logTPM, method="pearson")
    return(cor$estimate^2)
  }
}

get_cor_vec_us <- function(cut_vec, mir) {
  cor_vec <- sapply(cut_vec, get_cor_us, mir)
  return(cor_vec)
} 

```



# Get the cut_off correlation for mir122 (us)
```{r}
cut_vec <- seq(-2,0, length.out = 40)

cor <- get_cor_vec_us(cut_vec, mir = "mir122")
cor_df <- data.frame(cut_off = cut_vec, r2=cor)
cor_df1 <- cor_df

ggplot(cor_df, aes(x = cut_off, y = r2)) + 
  geom_line(size = 1) +
  theme_bw() +
  ylab('r^2') +
  ggtitle("mir122")

ggsave("cut_off_correlation_mir122.png")
gc()
```

# Get the cut_off correlation for mir138 (us)
```{r}
cut_vec <- seq(-2,0, length.out = 40)

cor <- get_cor_vec_us(cut_vec, mir = "mir138")
cor_df <- data.frame(cut_off = cut_vec, r2=cor)
cor_df2 <- cor_df

ggplot(cor_df, aes(x = cut_off, y = r2)) + 
  geom_line(size = 1) +
  theme_bw() +
  ylab('r^2') +
  ggtitle("mir138")

ggsave("cut_off_correlation_mir138.png")
gc()
```

# Get the cut_off correlation for mir216a (us)
```{r}
cut_vec <- seq(-2,0, length.out = 40)

cor <- get_cor_vec_us(cut_vec, mir = "mir216a")
cor_df <- data.frame(cut_off = cut_vec, r2=cor)
cor_df3 <- cor_df

ggplot(cor_df, aes(x = cut_off, y = r2)) + 
  geom_line(size = 1) +
  theme_bw() +
  ylab('r^2') +
  ggtitle("mir216a")

ggsave("cut_off_correlation_mir216a.png")
gc()
```



# Get all cut-off values
```{r}
# Get all files
seeds <- gsub("\\.txt", "", list.files("/mnt/schratt/miRNA_KD/EnrichMir_Work/Aggregate_fg/predictions_anB/", full.names = F))

# relate different miRNA IDs
mirs_alt <- gsub("hsa-", "", seeds)
mirs_alt <- gsub("-[35]p.*", "", mirs_alt)
mirs_alt <- gsub("R-", "r", mirs_alt)

seeds[seeds == "hsa-miR-133-3p"] <- "hsa-miR-133a-3p"
seeds[seeds == "hsa-miR-184-3p"] <- "hsa-miR-184"
names(mirs_alt) <- seeds


# get optimal for all mirs
cut_off_list <- list()
cut_vec <- seq(-2,0, length.out = 40)
for(mirna in mirs_alt) {
  cor <- get_cor_vec_us(cut_vec, mir = mirna)
  cor_df <- data.frame(cut_off = cut_vec, r2=cor)
  cor_df <- cor_df[which(cor_df$r2 > 0.99*max(cor_df$r2)),]
  cut_off <- min(cor_df$cut_off)
  cut_off_list[[mirna]]["cutoff"] <- cut_off
}

saveRDS(cut_off_list,"cut_off_list_99.rds")
```





# Get the cut_off correlation for mir122 (us) with a different ORF value
```{r}
cut_vec <- seq(-2,0, length.out = 40)

cor <- get_cor_vec_us(cut_vec, mir = "mir122")
cor_df <- data.frame(cut_off = cut_vec, r2=cor)
cor_df1 <- cor_df

ggplot(cor_df, aes(x = cut_off, y = r2)) + 
  geom_line(size = 1) +
  theme_bw() +
  ylab('r^2') +
  ggtitle("mir122")

ggsave("cut_off_correlation_mir122_ORF.png")
gc()
```




# Get the cut_off correlation for mir122 (us) with a different ORF value
```{r}
cut_vec <- seq(-2,0, length.out = 40)

cor <- get_cor_vec_us(cut_vec, mir = "mir122")
cor_df <- data.frame(cut_off = cut_vec, r2=cor)
cor_df1 <- cor_df

ggplot(cor_df, aes(x = cut_off, y = r2)) + 
  geom_line(size = 1) +
  theme_bw() +
  ylab('r^2') +
  ggtitle("mir122")

ggsave("cut_off_correlation_mir122_ORF2.png")
gc()
```



# Get the cut_off correlation for mir138 (us) with a different ORF value
```{r}
cut_vec <- seq(-2,0, length.out = 40)

cor <- get_cor_vec_us(cut_vec, mir = "mir138")
cor_df <- data.frame(cut_off = cut_vec, r2=cor)
cor_df1 <- cor_df

ggplot(cor_df, aes(x = cut_off, y = r2)) + 
  geom_line(size = 1) +
  theme_bw() +
  ylab('r^2') +
  ggtitle("mir138")

ggsave("cut_off_correlation_mir138_ORF.png")
gc()
```



# Get the cut_off correlation for mir216a (us) with a different ORF value
```{r}
cut_vec <- seq(-2,0, length.out = 40)

cor <- get_cor_vec_us(cut_vec, mir = "mir216a")
cor_df <- data.frame(cut_off = cut_vec, r2=cor)
cor_df1 <- cor_df

ggplot(cor_df, aes(x = cut_off, y = r2)) + 
  geom_line(size = 1) +
  theme_bw() +
  ylab('r^2') +
  ggtitle("mir216a")

ggsave("cut_off_correlation_mir216a_ORF2.png")
gc()
```








# Get all cut-off values
```{r}
# Get all files
seeds <- gsub("\\.txt", "", list.files("/mnt/schratt/miRNA_KD/EnrichMir_Work/Aggregate_fg/predictions_anB/", full.names = F))

# relate different miRNA IDs
mirs_alt <- gsub("hsa-", "", seeds)
mirs_alt <- gsub("-[35]p.*", "", mirs_alt)
mirs_alt <- gsub("R-", "r", mirs_alt)

seeds[seeds == "hsa-miR-133-3p"] <- "hsa-miR-133a-3p"
seeds[seeds == "hsa-miR-184-3p"] <- "hsa-miR-184"
names(mirs_alt) <- seeds


# get optimal for all mirs
cut_off_list <- list()
cut_vec <- seq(-2,0, length.out = 40)
for(mirna in mirs_alt) {
  cor <- get_cor_vec_us(cut_vec, mir = mirna)
  cor_df <- data.frame(cut_off = cut_vec, r2=cor)
  cor_df <- cor_df[which(cor_df$r2 > 0.975*max(cor_df$r2)),]
  cut_off <- min(cor_df$cut_off)
  cut_off_list[[mirna]]["cutoff"] <- cut_off
}

saveRDS(cut_off_list,"cut_off_list_orf_97.rds")



# get optimal for all mirs
cut_off_list <- list()
cut_vec <- seq(-2,0, length.out = 40)
for(mirna in mirs_alt) {
  cor <- get_cor_vec_us(cut_vec, mir = mirna)
  cor_df <- data.frame(cut_off = cut_vec, r2=cor)
  cor_df <- cor_df[which(cor_df$r2 > 0.99*max(cor_df$r2)),]
  cut_off <- min(cor_df$cut_off)
  cut_off_list[[mirna]]["cutoff"] <- cut_off
}

saveRDS(cut_off_list,"cut_off_list_orf_99.rds")
```





# Correlation function for background coefficient
```{r}
get_cor_us_back <- function(coef_back, mir, return.raw = FALSE){
  
  # Get all files and connections
  m <- readRDS(file = "/mnt/schratt/miRNA_KD/ms_test/hsa.12mirs.HEK.fullScan.GR.rds")
  hek_tpm <- read.csv("/mnt/schratt/miRNA_KD/EnrichMir_Work/Aggregate_fg/bartel_data/GSE140218_HEK293FT_transfection_logtpm_batchnormalized.txt", sep="\t", stringsAsFactors = F, row.names = 1)
  seeds <- gsub("\\.txt", "", list.files("/mnt/schratt/miRNA_KD/EnrichMir_Work/Aggregate_fg/predictions_anB/", full.names = F))
  
  # relate different miRNA IDs
  mirs_alt <- gsub("hsa-", "", seeds)
  mirs_alt <- gsub("-[35]p.*", "", mirs_alt)
  mirs_alt <- gsub("R-", "r", mirs_alt)
  
  seeds[seeds == "hsa-miR-184-3p"] <- "hsa-miR-184"
  names(mirs_alt) <- seeds
    
  
  # Get mean-centered hek-values and the aggregation
  # 1) get the seed info
  mir_seeds <- names(mirs_alt)[mirs_alt==mir]
  # 2) get the tpm values per mir
  subs_mir <- names(hek_tpm)[names(hek_tpm) != mir]
  hek_mir <- data.frame(
    logTPM = hek_tpm[[mir]]-rowMeans(hek_tpm[subs_mir]),
    transcript_id = row.names(hek_tpm),
    stringsAsFactors = F,
    row.names = rownames(hek_tpm)
    ) 
  
  # 3) aggregate
  m_agg <- aggregateMatches_Biochem(e = m, coef_back = coef_back)
  m_agg_slim <- m_agg[,c(1,2,5)]
  m_repr <- pivot_wider(m_agg,id_cols = transcript, names_from = miRNA, values_from = repression, values_fill = list(repression = 0))
  m_repr <- column_to_rownames(m_repr, var = "transcript")

  # 4) get the correlation
  subs_mir2 <- names(mirs_alt)[mirs_alt!=mir]
  m_repr_mir <- m_repr[mir_seeds] - rowMeans(m_repr[subs_mir2], na.rm = TRUE)
  repr_mir <- merge(hek_mir,m_repr_mir,by = 0, all.x = TRUE )
  repr_mir[[mir_seeds]][is.na(repr_mir[[mir_seeds]])] <- 0
  if(return.raw) {
    return(repr_mir)
  }else{
    cor = cor.test(repr_mir[[mir_seeds]], repr_mir$logTPM, method="pearson")
    return(cor$estimate^2)
  }
}

get_cor_vec_us_back <- function(coef_back_vec, mir) {
  cor_vec <- sapply(coef_back_vec, get_cor_us_back, mir)
  return(cor_vec)
} 

```




# Get the cut_off correlation for mir138 (us) with optimized background coefficient
```{r}
cut_vec <- seq(-2,0, length.out = 40)

cor <- get_cor_vec_us(cut_vec, mir = "mir138")
cor_df <- data.frame(cut_off = cut_vec, r2=cor)
cor_df1 <- cor_df
cor_df1$type <- "orf_cut_off '+ c'"


coef_back_vec <- seq(-3,0, length.out = 40)
cor <- get_cor_vec_us_back(coef_back_vec, mir = "mir138")
cor_df <- data.frame(coef_back = coef_back_vec, r2=cor)
cor_df2 <- cor_df
cor_df2$type <- "cut_off = 0.3 // coef_back"

cor_df <- rbind(cor_df1,cor_df2)


p1 <- ggplot(cor_df, aes(x = coef, y = r2, color = type)) + 
  geom_line(size = 1) +
  theme_bw() +
  ylab('r^2') +
  ggtitle("mir138")

#ggsave("cut_off_correlation_mir138_ORF.png")
gc()
```





# Comparing indices, this was for a global cut_off
```{r}
m138_0 <- get_cor_us(0,mir = "mir138",return.raw = TRUE)
m138_1 <- get_cor_us(-1,mir = "mir138",return.raw = TRUE)

m138_0 <- m138_0[order(m138_0$`hsa-miR-138-5p`),]
m138_0$index_0 <- seq_along(m138_0$Row.names)

m138_1 <- m138_1[order(m138_1$`hsa-miR-138-5p`),]
m138_1$index_1 <- seq_along(m138_1$Row.names)

m138 <- merge(m138_0,m138_1,by= "Row.names")

m138_03 <- get_cor_us(-0.3,mir = "mir138",return.raw = TRUE)
m138_03 <- m138_03[order(m138_03$`hsa-miR-138-5p`),]
m138_03$index_03 <- seq_along(m138_03$Row.names)

m138 <- merge(m138,m138_03, by="Row.names")

plot(m138$index_0,m138$index_03)
plot(m138$index_0,m138$index_1)
```








# Comparing indices, this is with the orf_cut_off
```{r}
m138_0 <- get_cor_us(0,mir = "mir138",return.raw = TRUE)
m138_1 <- get_cor_us(-1,mir = "mir138",return.raw = TRUE)

m138_0 <- m138_0[order(m138_0$`hsa-miR-138-5p`),]
m138_0$index_0 <- seq_along(m138_0$Row.names)

m138_1 <- m138_1[order(m138_1$`hsa-miR-138-5p`),]
m138_1$index_1 <- seq_along(m138_1$Row.names)

m138 <- merge(m138_0,m138_1,by= "Row.names")

m138_03 <- get_cor_us(-0.3,mir = "mir138",return.raw = TRUE)
m138_03 <- m138_03[order(m138_03$`hsa-miR-138-5p`),]
m138_03$index_03 <- seq_along(m138_03$Row.names)

m138 <- merge(m138,m138_03, by="Row.names")

plot(m138$index_0,m138$index_03)
plot(m138$index_0,m138$index_1)
```



# Comparing indices, this is with the orf_cut_off + c/2
```{r}
m138_0 <- get_cor_us(0,mir = "mir138",return.raw = TRUE)
m138_1 <- get_cor_us(-1,mir = "mir138",return.raw = TRUE)

m138_0 <- m138_0[order(m138_0$`hsa-miR-138-5p`),]
m138_0$index_0 <- seq_along(m138_0$Row.names)

m138_1 <- m138_1[order(m138_1$`hsa-miR-138-5p`),]
m138_1$index_1 <- seq_along(m138_1$Row.names)

m138 <- merge(m138_0,m138_1,by= "Row.names")

m138_03 <- get_cor_us(-0.3,mir = "mir138",return.raw = TRUE)
m138_03 <- m138_03[order(m138_03$`hsa-miR-138-5p`),]
m138_03$index_03 <- seq_along(m138_03$Row.names)

m138 <- merge(m138,m138_03, by="Row.names")

plot(m138$index_0,m138$index_03)
plot(m138$index_0,m138$index_1)
```



# To do a pie chart
```{r}
e <- readRDS(file = "/mnt/schratt/miRNA_KD/ms_test/hsa.12mirs.HEK.fullScan.GR.rds")
m <- as.data.frame(mcols(e))
m$transcript <- as.factor(seqnames(e))
m <- as.data.table(m)

cut_off <- nrow(m[m$log_kd > -300,])/nrow(m)
rest <- 1 - nrow(m[m$log_kd > -300,])/nrow(m)

df <- data.frame("cut-off 0.3" = cut_off , "rest" = rest)
df <- data.frame(t(df))
df$group <- row.names(df)

ggplot(df, aes(x="", y=t.df., fill=group))+
  geom_bar(width = 1, stat = "identity") + 
  coord_polar("y", start=0) + 
  scale_fill_brewer(palette="Dark2")+
  theme_minimal()

```



